---
title: "Lab 6 - Classification and Regression Trees"
author: ""
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<!-- Note: All R code has to go inbetween the line that looks like ```{r} and the line that looks like ```!! -->

## Loading Packages

Run the code chunk below to load packages needed for this lab.

```{r}
library(dplyr)
library(ISLR)
library(rpart)
```

This lab is adapted from Exercise 8.9 in ISLR.

## Orange Juice Purchases

The `OJ` data frame that comes with the ISLR package "contains 1070 purchases where the customer either purchased Citrus Hill or Minute Maid Orange Juice. A number of characteristics of the customer and product are recorded."

```{r}
head(OJ)
dim(OJ)

set.seed(71490)
train_inds <- caret::createDataPartition(OJ$Purchase, p = 0.8)
OJ_train <- OJ %>% dplyr::slice(train_inds[[1]])
OJ_test <- OJ %>% dplyr::slice(-train_inds[[1]])
```

The `Purchase` variable specifies which brand of orange juice the customer purchased (CH for Citrus Hill or MM for Minute Maid).  See the help file (`?OJ`) for descriptions of the other variables.

#### Problem 1: Fit a classification tree to the training data with `Purchase` as the response.  Use cross-validation to select the penalty parameter `cp`.  You can have the train function do cross-validation for you, you don't need to implement cross-validation yourself.  Make a plot of classification accuracy vs. cp.

```{r}

```

#### Problem 2: What is the predicted value for a customer with the characteristics given in the data frame below?  You should know how to solve this problem using the `predict` function and by tracing through a picture of the estimated tree.

```{r}
test_customer_problem3 <- data.frame(
  WeekofPurchase = 245,
  StoreID = 7,
  PriceCH = 1.90, 
  PriceMM = 2.09,
  DiscCH = 0,
  DiscMM = 0,
  SpecialCH = 0,
  SpecialMM = 0, 
  LoyalCH = 0.58031,
  SalePriceMM = 2.09,
  SalePriceCH = 1.9,
  PriceDiff = 0.19,
  Store7 = factor("Yes", levels = c("No", "Yes")),
  PctDiscMM = 0,
  PctDiscCH = 0, 
  ListPriceDiff = 0.19,
  STORE = 0)
```

```{r}

```

#### Problem 3: Find the test set error rate for the classification tree.

```{r}

```
